User-level Grid Monitoring with Inca 2

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
changed scalability section title
added acknowledgements


git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6619 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

To reduce the security risk of Inca, all Inca components communicate with each
other using SSL by default.  Sensitive information such as passwords is
encrypted before being stored to disk on the agent.  To handle reporters that
require a valid proxy credential to execute, the reporter manager fetches a
short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
administrator) and then destroys the proxy once the reporter has completed.
MyProxy authentication information is fetched from the agent each time a proxy
credential is needed and then cleared from memory.  Generating short-term 
proxies only when needed is more secure than maintaining long-term
credentials and is easier to manage.

\SubSection{Scalability}

@@

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON~\cite{geon} have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  Forwarding is not yet implemented 
in Inca 2.

@@

This work was supported by the following NSF grants:  Cooperative Agreement
Award \#0503944 SCI: TeraGrid Resource Partners,

>>>>

To provide for security, all Inca components communicate with each other using
SSL, and sensitive information is encrypted before being stored to disk.  To
handle reporters that
require a proxy credential to execute, the reporter manager fetches a
short-term proxy from a MyProxy~\cite{myproxy} server (as specified by an Inca
administrator), then destroys the proxy once the reporter has completed.
MyProxy authentication information is fetched from the agent each time a proxy
credential is needed and then cleared from memory.  Generating short-term 
proxies as needed is more secure than maintaining long-term
credentials and is easier to manage.

\SubSection{Coordinating Inca Deployments}

@@

A planned extension to Inca 2 supports the distribution of control and storage
workload among multiple Inca components.  Figure~\ref{tg_coord_fig} shows a
scenario where two Inca deployments coordinate with each other.  This could
occur in application communities like GEON~\cite{geon}, which maintains its
own Grid but also has access to TeraGrid resources.   Running two Inca
deployments independently could result in duplicate testing.  Instead, we plan
to eliminate redundancy by allowing multiple deployments to coordinate suite
execution.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  This extension is also expected
to provide the mechanisms for scalability and fault tolerance in the Inca
system.

@@

The authors would like to thank Denis Girou and David Spence for providing
details for the DEISA and NGS Inca deployments respectively.  This work was
supported by NSF grants SCI-0503944, SCI-0438741, and SCI-0503697.
